The Solar System: an Exercise in Numerical Integration \\ \hrulefill\small{ FYS3150: Computational Physics }\hrulefill

### 2016-10-23 Project3/article/article.tex
Minor code changes
Added some figures to article

@@

>>>>

\begin{figure}[ht]
	\centering
	\textbf{Comparison of Euler-Cromer and Velocity Verlet}
	\includegraphics[width=0.99\textwidth]{../figures/earthcompare.png}
	\label{fig:earthcompare}
	\caption{Figure showing the difference in precision between the Euler-Cromer method (left) and the velocity Verlet method (right). The time step is $dt=10^{-2}$ and the number of points is $N=10^6$}
\end{figure}

\begin{figure}[ht]
	\centering
	\textbf{Earth Escape Velocity}
	\includegraphics[width=0.9\textwidth]{../figures/earthescape.png}
	\caption{Illustration of Earth escaping orbit at $\sqrt{8}\pi AU/yr$}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\textbf{Earth, Sun and Jupiter}
	\includegraphics[width=0.99\textwidth]{../figures/threebody.png}
	\caption{Model outcome for a Jupiter with different masses. Top left: Normal mass. Top right: Jupiter mass $10\times$ normal. Bottom: Jupiter mass $1000\times$ normal, in 2D (left) and 3D (right)}
\end{figure}
